\begin{thebibliography}{10}

\bibitem{book}
{Bing Liu}, {\em Sentiment Analysis and Opinion Mining}.
\newblock 2012.

\bibitem{url:1}
\emph{``Social data gets the {X-Factor}.''}
  \url{http://www.brandwatch.com/2013/12/social-data-gets-the-x-factor/}.
\newblock Online; accessed 17-Apr-2015.

\bibitem{url:2}
\emph{``Deeply moving: Deep learning for sentiment analysis.''}
  \url{http://nlp.stanford.edu/sentiment/}.
\newblock Online; accessed 24-March-2015.

\bibitem{puspak}
A.~Ramteke, A.~Malu, P.~Bhattacharyya, and J.~S. Nath, ``Detecting turnarounds
  in sentiment analysis: Thwarting.,'' in {\em ACL (2)}, pp.~860--865, The
  Association for Computer Linguistics, 2013.

\bibitem{tu}
B.~Pang, L.~Lee, and S.~Vaithyanathan, ``Thumbs up? sentiment classification
  using machine learning techniques,'' in {\em Proceedings of EMNLP},
  pp.~79--86, 2002.

\bibitem{ir}
O.~Vectomova, K.~Suleman, and J.~Thomas, ``An information retrieval-based
  approach to determining contextual opinion polarity of words,'' in {\em
  Proceedings of the 36th European Conference on Information Retrieval (ECIR),
  Amsterdam}, 2014.

\bibitem{saif}
S.~M. Mohammad, S.~Kiritchenko, and X.~Zhu, ``{NRC-Canada}: Building the
  state-of-the-art in sentiment analysis of tweets.,'' {\em CoRR},
  vol.~abs/1308.6242, 2013.

\bibitem{omg}
E.~Kouloumpis, T.~Wilson, and J.~Moore, ``Twitter sentiment analysis: The good
  the bad and the {OMG}!,'' in {\em ICWSM} (L.~A. Adamic, R.~A. Baeza-Yates, and
  S.~Counts, eds.), The AAAI Press, 2011.

\bibitem{tweebo}
L.~Kong, N.~Schneider, S.~Swayamdipta, A.~Bhatia, C.~Dyer, and N.~A. Smith, ``A
  dependency parser for tweets,'' in {\em Proceedings of the 2014 Conference on
  Empirical Methods in Natural Language Processing (EMNLP)}, 2014.

\bibitem{user}
C.~Tan, L.~Lee, J.~Tang, L.~Jiang, M.~Zhou, and P.~L. 0001, ``User-level
  sentiment analysis incorporating social networks,'' {\em CoRR},
  vol.~abs/1109.6018, 2011.

\bibitem{url:3}
\emph{``The six types of social media.''}
  \url{http://timgrahl.com/the-6-types-of-social-media/}.
\newblock Online; accessed 17-Apr-2015.

\end{thebibliography}